Genomic prediction associated with citizen science for early selection and improvement in durum wheat

### 2019-07-25 manuscript/manuscript.Rmd
plmodel

# Research questions:

* Does farmers' evaluations associated with genes provide better predictions on varietal performance then station-only data?
* Can the GxE estimates be improved by farmers' evaluations associated to SNP markers?
* Can the combination of genomic and citizen science provide new insights in which traits farmers prioritise or which areas of the genome play a role?

>>>>

# Introduction 
- wheat is the second largest ceral grain cultivated worldwide
- durum wheat is mainly used for pasta production 
- is a cultivar evolved from domesticated emmer wheat 
- most of its genetic diversity is found in Ethiopia 
- even though most farmers are exposed to a small set of Mediterranean modern varieties
-
